---
title: "Example - Ice Cream Ratings"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(gsheet)
library(tidyverse)
library(fastDummies)

data <- as_tibble(gsheet2tbl("https://docs.google.com/spreadsheets/d/1QH5XDEUEmBGp2ZzO7OQS0T1vSELIjFAi2gTmnqokoMg/edit#gid=0"))

data$Sweetner <- str_remove(data$Sweetner, "[%]")
  data$Sweetner <- as.numeric(data$Sweetner)

data$MilkFat <- str_remove(data$MilkFat, "[%]")
  data$MilkFat <- as.numeric(data$MilkFat)
  
data$Air <- str_remove(data$Air, "[%]")
  data$Air <- as.numeric(data$Air)
```

Commercially produced ice cream is made from a mixture of ingredients: a minimum of 10% milk fat, 9—12% milk solids, 12—16% sweetener, 0.2—0.5% stabilizers and emulsifiers, and 55—64% water. Air is incorporated with the above ingredients during the mixing process. The finest ice creams have between 3% and 15% air.

A food scientist is investigating how varying the amounts of the above ingredients impacts the sensory rating of the final product. The scientist decides to use three levels of milk fat: 10%, 12%, and 15%; three amounts of air: 5%, 10%, 15%; and two levels of sweeteners: 12%, 16%.

## Categorical Predictors

#### Create Dummy Variables

```{r}
data <- dummy_cols(data, select_columns = c("Sweetner", "MilkFat", "Air"))
```

#### Construct the Model with All Main Effects

```{r}
m <- lm(Ratings ~ Sweetner_12 + MilkFat_12 + MilkFat_15 + Air_10 + Air_15, data = data)

m <- lm(Ratings ~ Sweetner + Air + MilkFat, data = data)

summary(m)
```

#### Is Sweetner a Significant Predictor of Sensory Rating?

```{r}

```

**Hypotheses**


**Test Statistic**


***p*-value**


**Rejection Region**


**Conclusion and Interpretation**

#### Is Milk Fat a Significant Predictor of Sensory Rating?

```{r}

```

**Hypotheses**


**Test Statistic**


***p*-value**


**Rejection Region**


**Conclusion and Interpretation**

#### Is Air a Significant Predictor of Sensory Rating?

```{r}

```

**Hypotheses**


**Test Statistic**


***p*-value**


**Rejection Region**


**Conclusion and Interpretation**

## Visualization - Categorical Predictors Only

## Continuous Predictors

#### Construct the Model with All Main Effects

#### Is Sweetner a Significant Predictor of Sensory Rating?

```{r}

```

**Hypotheses**


**Test Statistic**


***p*-value**


**Rejection Region**


**Conclusion and Interpretation**

#### Is Milk Fat a Significant Predictor of Sensory Rating?

```{r}

```

**Hypotheses**


**Test Statistic**


***p*-value**


**Rejection Region**


**Conclusion and Interpretation**

#### Is Air a Significant Predictor of Sensory Rating?

```{r}

```

**Hypotheses**


**Test Statistic**


***p*-value**


**Rejection Region**


**Conclusion and Interpretation**

## Interaction Terms 

#### Construct the Model with the Three-Way Interaction -- Categorical Predictors

```{r}

```

#### Testing the Three-Way Interaction Between Sweetner, Milk Fat, and Air

**Hypotheses**


**Test Statistic**


***p*-value**


**Rejection Region**


**Conclusion and Interpretation**

#### Construct the Model with the Three-Way Interaction -- Continuous Predictors

```{r}

```

#### Testing the Three-Way Interaction Between Sweetner, Milk Fat, and Air

**Hypotheses**


**Test Statistic**


***p*-value**


**Rejection Region**


**Conclusion and Interpretation**


#### Remove the Three-Way Interaction

```{r}

```


#### Test Significance of All Interaction Terms

```{r}

```

**Hypotheses**


**Test Statistic**


***p*-value**


**Rejection Region**


**Conclusion and Interpretation**


#### Examining All Two-Way Interactions

```{r}

```
 
Can we remove the non-significant interactions at the same time?

```{r}

```

Is there anything else we can remove?

```{r}

```

#### Final Model

```{r}

```

## Visualization - Interaction

We now will construct a visualization. First, we must decide what goes where on the graph. Let's put milk fat on the *x* axis and create lines with air. Let's remind ourselves of the levels of air:

```{r}

```

We will use levels 5, 10, and 15 in our predictions. Note that if this were truly a continuous variable, we would want to look at the 25th percentile, the median, and the 75th percentile. 

```{r}

```

We also will color our observations on the graph by the level of sweetner. We first need to turn it back into a factor variable,

```{r}

```

Now we are ready to graph,

```{r}

```

We can see that as milk fat increases...

We can also examine this the other way, with air on the *x*-axis and milk fat defining the lines. Let's look at the levels of milk fat.

```{r}

```

We will use levels 10, 12, and 15 in our predictions. Like we noted for air, if this were truly a continuous variable, we would want to look at the 25th percentile, the median, and the 75th percentile.

```{r}

```

Now we are ready to graph,

```{r}

```

We can see that as air increases....