---
title: "Q11 Replacement - Ice Cream Ratings Example"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(gsheet)
library(tidyverse)
library(fastDummies)

data <- as_tibble(gsheet2tbl("https://docs.google.com/spreadsheets/d/1QH5XDEUEmBGp2ZzO7OQS0T1vSELIjFAi2gTmnqokoMg/edit#gid=0"))

data$Sweetner <- str_remove(data$Sweetner, "[%]")
  data$Sweetner2 <- as.numeric(data$Sweetner)

data$MilkFat <- str_remove(data$MilkFat, "[%]")
  data$MilkFat2 <- as.numeric(data$MilkFat)
  
data$Air <- str_remove(data$Air, "[%]")
  data$Air2 <- as.numeric(data$Air)
```

Commercially produced ice cream is made from a mixture of ingredients: a minimum of 10% milk fat, 9—12% milk solids, 12—16% sweetener, 0.2—0.5% stabilizers and emulsifiers, and 55—64% water. Air is incorporated with the above ingredients during the mixing process. The finest ice creams have between 3% and 15% air.

A food scientist is investigating how varying the amounts of the above ingredients impacts the sensory rating of the final product. The scientist decides to use three levels of milk fat: 10%, 12%, and 15%; three amounts of air: 5%, 10%, 15%; and two levels of sweeteners: 12%, 16%.

## Categorical Predictors

#### Create Dummy Variables

```{r}
data <- dummy_cols(data, select_columns = c("Sweetner", "MilkFat", "Air"))
```

#### Construct the Model with All Main Effects

```{r}
# trial - include all of the dummy variables
m1 <- lm(Ratings ~ Sweetner_12 + Sweetner_16 +
                  MilkFat_10 + MilkFat_12 + MilkFat_15 +
                  Air_5 + Air_10 + Air_15,
        data = data)
summary(m1)

# exclude the reference groups
m2 <- lm(Ratings ~ Sweetner_16 +
                   MilkFat_12 + MilkFat_15 +
                   Air_10 + Air_15,
        data = data)
summary(m2)
```

\[ \hat{\text{rating}} = 26.48 + 1.93 \text{sweet}_{16} + 5.33 \text{fat}_{12} + 2.00 \text{fat}_{15} + 5.67 \text{air}_{10} - 0.67 \text{air}_{15}\]

#### Is Sweetner a Significant Predictor of Sensory Rating?

```{r}
summary(m2)
```

**Hypotheses**

  - $H_0: \ \beta_{\text{sweet}_{16}} = 0$
  - $H_1: \ \beta_{\text{sweet}_{16}} \ne 0$

**Test Statistic**

  - $t_0 = 1.985$

***p*-value**

  - $p = 0.0529$

**Rejection Region**

  - Reject $H_0$ if $p < \alpha$; $\alpha = 0.05$

**Conclusion and Interpretation**

  - FTR $H_0$. There is not sufficient evidence to suggest that sweetner is predictive of ice cream sensory rating.

#### Is Milk Fat a Significant Predictor of Sensory Rating?

```{r}
full <- m2
reduced <- lm(Ratings ~ Sweetner_16 +
                        Air_10 + Air_15,
              data = data)
anova(reduced, full)
```

**Hypotheses**

  - $H_0: \ \beta_{\text{fat}_{12}} = \beta_{\text{fat}_{15}} = 0$
  - $H_1:$ at least one $\beta_i \ne 0$

**Test Statistic**

  - $F_0 = 10.283$

***p*-value**

  - $p < 0.001$

**Rejection Region**

  - Reject $H_0$ if $p < \alpha$; $\alpha=0.05$

**Conclusion and Interpretation**

  - Reject $H_0$. There is sufficient evidence to suggest that milk fat is a significant predictor of ice cream sensory ratings.

#### Is Air a Significant Predictor of Sensory Rating?

```{r}
full <- m2
reduced <- lm(Ratings ~ Sweetner_16 +
                        MilkFat_12 + MilkFat_15,
              data = data)
anova(reduced, full)
```

**Hypotheses**

**Test Statistic**

***p*-value**

**Rejection Region**

**Conclusion and Interpretation**

## Visualization - Categorical Predictors Only

We have a model with three categorical predictors.

Ratings will go on the *Y*-axis. This is always the outcome of interest.

Milk fat will go on the *X*-axis. This should be something we can treat as continuous; if you have multiple to choose from, choose the one with the most categories.

We can combine the other two predictors (air and sweetener) to create lines:
- Air 5, Sweetener 12
- Air 5, Sweetener 16
- Air 10, Sweetener 12
- Air 10, Sweetener 16
- Air 15, Sweetener 12
- Air 15, Sweetener 16

```{r}
c <- coefficients(m2)

data <- data %>%
  mutate(y_s12_a5 = c["(Intercept)"] + c["Sweetner_16"]*0 + 
           c["MilkFat_12"]*MilkFat_12 + c["MilkFat_15"]*MilkFat_15 +
           c["Air_10"]*0 + c["Air_15"]*0,
         y_s12_a10 = c["(Intercept)"] + c["Sweetner_16"]*0 + 
           c["MilkFat_12"]*MilkFat_12 + c["MilkFat_15"]*MilkFat_15 +
           c["Air_10"]*1 + c["Air_15"]*0,
         y_s12_a15 = c["(Intercept)"] + c["Sweetner_16"]*0 + 
           c["MilkFat_12"]*MilkFat_12 + c["MilkFat_15"]*MilkFat_15 +
           c["Air_10"]*0 + c["Air_15"]*1)

data %>% ggplot(aes(x = MilkFat2, y = Ratings)) +
  geom_point() +
  geom_line(aes(y = y_s12_a5), color = "pink") +
  geom_line(aes(y = y_s12_a10), color = "blue") +
  geom_line(aes(y = y_s12_a15), color = "purple") +
  theme_minimal() +
  ggtitle("Plot for Sweetner of 12")

# you add the plot for Sweetner of 16 :)
```

## Continuous Predictors

#### Construct the Model with All Main Effects

```{r}

```

#### Is Sweetner a Significant Predictor of Sensory Rating?

```{r}

```

**Hypotheses**

**Test Statistic**

***p*-value**

**Rejection Region**

**Conclusion and Interpretation**

#### Is Milk Fat a Significant Predictor of Sensory Rating?

```{r}

```

**Hypotheses**

**Test Statistic**

***p*-value**

**Rejection Region**

**Conclusion and Interpretation**

#### Is Air a Significant Predictor of Sensory Rating?

```{r}

```

**Hypotheses**

**Test Statistic**

***p*-value**

**Rejection Region**

**Conclusion and Interpretation**

## Interaction Terms 

#### Construct the Model with the Three-Way Interaction -- Categorical Predictors

```{r}
m3 <- lm(Ratings ~ Sweetner_16 + MilkFat_12 + MilkFat_15 + Air_10 + Air_15 +
           Sweetner_16:MilkFat_12 + Sweetner_16:MilkFat_15 + Sweetner_16:Air_10 + Sweetner_16:Air_15 +
           MilkFat_12:Air_10 + MilkFat_12:Air_15 +
           MilkFat_15:Air_10 + MilkFat_15:Air_15 +
           Sweetner_16:MilkFat_12:Air_10 +
           Sweetner_16:MilkFat_12:Air_15 +
           Sweetner_16:MilkFat_15:Air_10 +
           Sweetner_16:MilkFat_15:Air_15,
         data = data)

summary(m3)
```

#### Testing the Three-Way Interaction Between Sweetner, Milk Fat, and Air

```{r}
full <- m3
reduced <- lm(Ratings ~ Sweetner_16 + MilkFat_12 + MilkFat_15 + Air_10 + Air_15 +
           Sweetner_16:MilkFat_12 + Sweetner_16:MilkFat_15 + Sweetner_16:Air_10 + Sweetner_16:Air_15 +
           MilkFat_12:Air_10 + MilkFat_12:Air_15 +
           MilkFat_15:Air_10 + MilkFat_15:Air_15,
         data = data)
anova(reduced, full)
```

**Hypotheses**

**Test Statistic**

***p*-value**

**Rejection Region**

**Conclusion and Interpretation**

#### Construct the Model with the Three-Way Interaction -- Continuous Predictors

```{r}
m4 <- lm(Ratings ~ Sweetner2 + MilkFat2 + Air2 +
                   Sweetner2:MilkFat2 + Sweetner2:Air2 + MilkFat2:Air2 +
                   Sweetner2:MilkFat2:Air2, 
         data = data)
```

#### Testing the Three-Way Interaction Between Sweetner, Milk Fat, and Air

**Hypotheses**

**Test Statistic**

***p*-value**

**Rejection Region**

**Conclusion and Interpretation**

#### Remove the Three-Way Interaction

```{r}

```


#### Test Significance of All (Two-Way) Interaction Terms

```{r}

```

**Hypotheses**

**Test Statistic**

***p*-value**

**Rejection Region**

**Conclusion and Interpretation**

#### Examining All Two-Way Interactions
 
Can we remove the non-significant interactions at the same time?

```{r}

```

Is there anything else we can remove?

```{r}

```

#### Final Model

```{r}

```

## Visualization - Interaction

We now will construct a visualization. First, we must decide what goes where on the graph. Let's put milk fat on the *X*-axis and create lines with air. We will use levels 5, 10, and 15 in our predictions. We also will color our observations on the graph by the level of sweetner. 

Now we are ready to graph,

```{r}

```

We can see that as milk fat increases... [what happens?]

We can also examine this the other way, with air on the *X*-axis and milk fat defining the lines. We will use levels 10, 12, and 15 in our predictions. Like we noted for air, if this were truly a continuous variable, we would want to look at the 25th percentile, the median, and the 75th percentile.

Now we are ready to graph,

```{r}

```

We can see that as air increases.... [what happens?]