---
title: "Example - Ice Cream Ratings"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(gsheet)
library(tidyverse)
library(fastDummies)

data <- as_tibble(gsheet2tbl("https://docs.google.com/spreadsheets/d/1QH5XDEUEmBGp2ZzO7OQS0T1vSELIjFAi2gTmnqokoMg/edit#gid=0"))

data$Sweetner <- str_remove(data$Sweetner, "[%]")
  data$Sweetner <- as.numeric(data$Sweetner)

data$MilkFat <- str_remove(data$MilkFat, "[%]")
  data$MilkFat <- as.numeric(data$MilkFat)
  
data$Air <- str_remove(data$Air, "[%]")
  data$Air <- as.numeric(data$Air)
```

Commercially produced ice cream is made from a mixture of ingredients: a minimum of 10% milk fat, 9—12% milk solids, 12—16% sweetener, 0.2—0.5% stabilizers and emulsifiers, and 55—64% water. Air is incorporated with the above ingredients during the mixing process. The finest ice creams have between 3% and 15% air.

A food scientist is investigating how varying the amounts of the above ingredients impacts the sensory rating of the final product. The scientist decides to use three levels of milk fat: 10%, 12%, and 15%; three amounts of air: 5%, 10%, 15%; and two levels of sweeteners: 12%, 16%.

## Categorical Predictors

#### Create Dummy Variables

```{r}
data <- dummy_cols(data, select_columns = c("Sweetner", "MilkFat", "Air"))
```

#### Construct the Model with All Main Effects

```{r}
m <- lm(Ratings ~ Sweetner_12 + MilkFat_12 + MilkFat_15 + Air_10 + Air_15, data = data)

summary(m)
```

#### Is Sweetner a Significant Predictor of Sensory Rating?

```{r}
summary(m)
```

**Hypotheses**

&emsp; &emsp; $H_0: \ \beta_{\text{Sweetner}} = 0$ \\
&emsp; &emsp; $H_1: \ \beta_{\text{Sweetner}} \ne 0$

**Test Statistic**

&emsp; &emsp; $t_0 = -1.985$

***p*-value**

&emsp; &emsp; $p = 0.0529$

**Rejection Region**

&emsp; &emsp; Reject $H_0$ if $p < \alpha$; $\alpha = 0.05$.

**Conclusion and Interpretation**

&emsp; &emsp; FTR $H_0$. There is not sufficient evidence to suggest that sweetener is a predictor of sensory rating.

#### Is Milk Fat a Significant Predictor of Sensory Rating?

```{r}
full <- lm(Ratings ~ Sweetner_12 + MilkFat_12 + MilkFat_15 + Air_10 + Air_15, data = data)

reduced <- lm(Ratings ~ Sweetner_12 + Air_10 + Air_15, data = data)

anova(reduced, full)
```

**Hypotheses**

&emsp; &emsp; $H_0: \ \beta_{\text{MilkFat12}} = \beta_{\text{MilkFat15}} = 0 $ \\
&emsp; &emsp; $H_1:$ at least one $\beta_i$ is $\ne 0$ 

**Test Statistic**

&emsp; &emsp; $F_0 = 10.283$

***p*-value**

&emsp; &emsp; $p < 0.001$ 

**Rejection Region**

&emsp; &emsp; Reject $H_0$ if $p < \alpha$; $\alpha = 0.05$

**Conclusion and Interpretation**

&emsp; &emsp; Reject $H_0$. There is sufficient evidence to suggest that milk fat is a significant predictor of sensory rating. 

#### Is Air a Significant Predictor of Sensory Rating?

```{r}
full <- lm(Ratings ~ Sweetner_12 + MilkFat_12 + MilkFat_15 + Air_10 + Air_15, data = data)

reduced <- lm(Ratings ~ Sweetner_12 + MilkFat_12 + MilkFat_15, data = data)

anova(reduced, full)
```

**Hypotheses**

&emsp; &emsp; $H_0: \ \beta_{\text{Air10}} = \beta_{\text{Air15}} = 0 $ \\
&emsp; &emsp; $H_1:$ at least one $\beta_i$ is $\ne 0$ 

**Test Statistic**

&emsp; &emsp; $F_0 = 17.156$

***p*-value**

&emsp; &emsp; $p < 0.001$ 

**Rejection Region**

&emsp; &emsp; Reject $H_0$ if $p < \alpha$; $\alpha = 0.05$

**Conclusion and Interpretation**

&emsp; &emsp; Reject $H_0$. There is sufficient evidence to suggest that air is a significant predictor of sensory rating.

## Visualization - Categorical Predictors Only

We have a model with three categorical predictors.

Ratings will go on the Y axis. This is always the outcome of interest.

Milk fat will go on the X axis. This should be something we can treat as continuous; if you have multiple to choose from, choose the one with the most categories.

We can combine the other two predictors (air and sweetener) to create lines:
- Air 5, Sweetener 12
- Air 5, Sweetener 16
- Air 10, Sweetener 12
- Air 10, Sweetener 16
- Air 15, Sweetener 12
- Air 15, Sweetener 16

```{r}
c <- coefficients(m)

c

data <- data %>%
  mutate(y_s12_a5 = c["(Intercept)"] + c["Sweetner_12"]*1 + c["MilkFat_12"]*MilkFat_12 + c["MilkFat_15"]*MilkFat_15 +
           c["Air_10"]*0 + c["Air_15"]*0,
         y_s16_a5 = c["(Intercept)"] + c["Sweetner_12"]*0 + c["MilkFat_12"]*MilkFat_12 + c["MilkFat_15"]*MilkFat_15 +
           c["Air_10"]*0 + c["Air_15"]*0,
         y_s12_a10 = c["(Intercept)"] + c["Sweetner_12"]*1 + c["MilkFat_12"]*MilkFat_12 + c["MilkFat_15"]*MilkFat_15 +
           c["Air_10"]*1 + c["Air_15"]*0,
         y_s16_a10 = c["(Intercept)"] + c["Sweetner_12"]*0 + c["MilkFat_12"]*MilkFat_12 + c["MilkFat_15"]*MilkFat_15 +
           c["Air_10"]*1 + c["Air_15"]*0,
         y_s12_a15 = c["(Intercept)"] + c["Sweetner_12"]*1 + c["MilkFat_12"]*MilkFat_12 + c["MilkFat_15"]*MilkFat_15 +
           c["Air_10"]*0 + c["Air_15"]*1,
         y_s16_a15 = c["(Intercept)"] + c["Sweetner_12"]*0 + c["MilkFat_12"]*MilkFat_12 + c["MilkFat_15"]*MilkFat_15 +
           c["Air_10"]*0 + c["Air_15"]*1)

data %>% ggplot(aes(x = MilkFat, y = Ratings)) +
  geom_point() +
  geom_line(aes(y = y_s12_a5), color = "pink") + 
  geom_line(aes(y = y_s16_a5), color = "blue") +
  geom_line(aes(y = y_s12_a10), color = "green") + 
  geom_line(aes(y = y_s16_a10), color = "red") +
  geom_line(aes(y = y_s12_a15), color = "purple") + 
  geom_line(aes(y = y_s16_a15)) +
  theme_minimal()
```

## Continuous Predictors

#### Construct the Model with All Main Effects

#### Is Sweetner a Significant Predictor of Sensory Rating?

```{r}

```

**Hypotheses**


**Test Statistic**


***p*-value**


**Rejection Region**


**Conclusion and Interpretation**

#### Is Milk Fat a Significant Predictor of Sensory Rating?

```{r}

```

**Hypotheses**


**Test Statistic**


***p*-value**


**Rejection Region**


**Conclusion and Interpretation**

#### Is Air a Significant Predictor of Sensory Rating?

```{r}

```

**Hypotheses**


**Test Statistic**


***p*-value**


**Rejection Region**


**Conclusion and Interpretation**

## Interaction Terms 

#### Construct the Model with the Three-Way Interaction -- Categorical Predictors

```{r}
m <- lm(Ratings ~ Sweetner_16 + MilkFat_12 + MilkFat_15 + Air_10 + Air_15 +
        Sweetner_16:MilkFat_12 + Sweetner_16:MilkFat_15 +
          Sweetner_16:Air_10 + Sweetner_16:Air_15 +
          MilkFat_12:Air_10 + MilkFat_12:Air_15 +
          MilkFat_15:Air_10 + MilkFat_15:Air_15 +
          Sweetner_16:MilkFat_15:Air_15 + 
          Sweetner_16:MilkFat_15:Air_10 +
          Sweetner_16:MilkFat_12:Air_15 +
          Sweetner_16:MilkFat_12:Air_10, data = data)

summary(m)

```

#### Testing the Three-Way Interaction Between Sweetner, Milk Fat, and Air

```{r}
full <- lm(Ratings ~ Sweetner_16 + MilkFat_12 + MilkFat_15 + Air_10 + Air_15 +
        Sweetner_16:MilkFat_12 + Sweetner_16:MilkFat_15 +
          Sweetner_16:Air_10 + Sweetner_16:Air_15 +
          MilkFat_12:Air_10 + MilkFat_12:Air_15 +
          MilkFat_15:Air_10 + MilkFat_15:Air_15 +
          Sweetner_16:MilkFat_15:Air_15 + 
          Sweetner_16:MilkFat_15:Air_10 +
          Sweetner_16:MilkFat_12:Air_15 +
          Sweetner_16:MilkFat_12:Air_10, data = data)

reduced <- lm(Ratings ~ Sweetner_16 + MilkFat_12 + MilkFat_15 + Air_10 + Air_15 +
        Sweetner_16:MilkFat_12 + Sweetner_16:MilkFat_15 +
          Sweetner_16:Air_10 + Sweetner_16:Air_15 +
          MilkFat_12:Air_10 + MilkFat_12:Air_15 +
          MilkFat_15:Air_10 + MilkFat_15:Air_15, data = data)

anova(reduced, full)
```

**Hypotheses**


**Test Statistic**


***p*-value**


**Rejection Region**


**Conclusion and Interpretation**

#### Construct the Model with the Three-Way Interaction -- Continuous Predictors

```{r}
m <- lm(Ratings ~ Sweetner + MilkFat + Air + Sweetner:MilkFat + Sweetner:Air + MilkFat:Air + Sweetner:MilkFat:Air, data = data)

m <- lm(Ratings ~ Sweetner*MilkFat*Air, data = data)

summary(m)
```

#### Testing the Three-Way Interaction Between Sweetner, Milk Fat, and Air

**Hypotheses**


**Test Statistic**


***p*-value**


**Rejection Region**


**Conclusion and Interpretation**


#### Remove the Three-Way Interaction

```{r}
m <- lm(Ratings ~ Sweetner + MilkFat + Air + Sweetner:MilkFat + Sweetner:Air + MilkFat:Air, data = data)

summary(m)
```


#### Test Significance of All Interaction Terms

```{r}

```

**Hypotheses**


**Test Statistic**


***p*-value**


**Rejection Region**


**Conclusion and Interpretation**


#### Examining All Two-Way Interactions

```{r}

```
 
Can we remove the non-significant interactions at the same time?

```{r}
full <- lm(Ratings ~ Sweetner + MilkFat + Air + Sweetner:MilkFat + Sweetner:Air + MilkFat:Air, data = data)

reduced <- lm(Ratings ~ Sweetner + MilkFat + Air + MilkFat:Air, data = data)

anova(reduced, full)

summary(m)

m <- lm(Ratings ~ Sweetner + MilkFat + Air + MilkFat:Air, data = data)

summary(m)

```

Is there anything else we can remove?

```{r}
m <- lm(Ratings ~  MilkFat + Air + MilkFat:Air, data = data)
```

#### Final Model

```{r}
m <- lm(Ratings ~  MilkFat + Air + MilkFat:Air, data = data)
summary(m)
```

## Visualization - Interaction

We now will construct a visualization. First, we must decide what goes where on the graph. Let's put milk fat on the *x* axis and create lines with air. Let's remind ourselves of the levels of air:

```{r}

```

We will use levels 5, 10, and 15 in our predictions. Note that if this were truly a continuous variable, we would want to look at the 25th percentile, the median, and the 75th percentile. 

```{r}

```

We also will color our observations on the graph by the level of sweetner. We first need to turn it back into a factor variable,

```{r}

```

Now we are ready to graph,

```{r}

```

We can see that as milk fat increases...

We can also examine this the other way, with air on the *x*-axis and milk fat defining the lines. Let's look at the levels of milk fat.

```{r}

```

We will use levels 10, 12, and 15 in our predictions. Like we noted for air, if this were truly a continuous variable, we would want to look at the 25th percentile, the median, and the 75th percentile.

```{r}

```

Now we are ready to graph,

```{r}

```

We can see that as air increases....