---
title: "STA6235 Week 2"
author: "Your Name Here"
format: 
  html:
    self-contained: true
execute:
  echo: true
  warning: false
  message: false
  error: true
editor: source
---

**1. Pull in the [Palmer penguins dataset](https://allisonhorst.github.io/palmerpenguins/).**

```{r}

```

**2. Find the mean and standard deviation for the body mass of penguins (*body_mass_g*). Please use the `summarize()` function from `tidyverse`.**

```{r}

```

**3. Find the mean and standard deviation for the body mass of penguins (*body_mass_g*), split by species of penguin (*species*). Please use the `group_by()` and `summarize()` functions from `tidyverse`.**

```{r}

```

**4. Construct 95% confidence intervals for the body mass of penguins (*body_mass_g*) for each species of penguin (*species*).**

```{r}

```

**5. Construct a scatterplot with body mass (*body_mass_g*) on the *y*-axis, flipper length (*flipper_length_mm*) on the *x*-axis, and the markers (dots) colored by species of penguin (*species*).**

```{r}

```

**6. Model penguin body mass (*body_mass_g*) as a function of flipper length (*flipper_length_mm*) and bill length (*bill_length_mm*). Remember to state the resulting regression model.**

```{r}

```

**7. Create a table that has Estimate (95% CI) and *p*-Value as columns; every predictor in the regression model will have a row. See [Table 2 in this paper](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC4742426/) for an example.**

<!-- Hint: tablesgenerator.com is wonderful for helping us create tables! Either markdown or HTML tables will work. There is more flexibility with HTML tables in terms of formatting :) -->

```{r}

```

**8. Use the appropriate hypothesis test to determine if this is a significant regression line. Test at the $\alpha=0.05$ level. Remember to typeset your results.**

```{r}

```

**9. Use the appropriate hypothesis test(s) to determine which, if any, are significant predictors of penguin body mass. Test at the $\alpha=0.05$ level. Remember to typeset your results.**

**10. Create a data visualization for your regression model. Use the plot in question 5 as a starting point and overlay a regression line. (This means that only flipper length will vary and you will need to hold bill length constant.)**

```{r}

```


















