---
title: "STA6235 Week 6"
author: "Your Name Here"
format: 
  html:
    self-contained: true
execute:
  echo: true
  warning: false
  message: false
  error: true
editor: source
---

**1. Import the JHS data. (This is in Week 1's module on Canvas.)**

```{r}

```

**2. Professional development (data management): Create a variable called *smoking* that combines *currentSmoker* (1 = current smoker, 0 = not current smoker) and *everSmoker* (1 = has smoked at least 200 cigarettes in their lifetime, 0 = has not smoked more than 200 cigarettes) into a three level variable, where 1 = current smoker, 2 = former smoker, 3 = never smoker.**

```{r}

```

**3. Using the normal distribution, model HbA1c (*HbA1c*) as a function of age (*age*), waist circumference (cm; *waist*), hypertension medication use (*BPmeds*; 1 = takes blood pressure lowering medication, 0 = does not take blood pressure lowering drugs), smoking status (*smoking*), the interaction between age and hypertension medication use, and the interaction between age and smoking status. Remember to report the final model.**

```{r}

```

**4. Provide appropriate interpretations for the slopes in the above model for someone with *age* = 45. Algebraically simplify the model so that you can interpret the main effects, skipping the interpretation for age.**



**5. Using the gamma distribution, model HbA1c (*HbA1c*) as a function of age (*age*), waist circumference (cm; *waist*), hypertension medication use (*BPmeds*; 1 = takes blood pressure lowering medication, 0 = does not take blood pressure lowering drugs), smoking status (*smoking*), the interaction between age and hypertension medication use, and the interaction between age and smoking status. Remember to report the final model.**



**6. Provide appropriate interpretations for the slopes in the above model for someone with *age* = 45. Algebraically simplify the model so that you can interpret the main effects, skipping the interpretation for age.**



**7. Assess the relevant assumptions to determine if gamma regression is necessary. Remember to draw a conclusion (in words).**

```{r}

```





