---
title: "STA6235 Week 8"
author: "Your Name Here"
format: 
  html:
    self-contained: true
execute:
  echo: true
  warning: false
  message: false
  error: true
editor: source
---

This week we will use the [Scooby Doo episode data](https://github.com/rfordatascience/tidytuesday/tree/718b0cd36672e14457f15cba7f061c4cf7caf9f6/data/2021/2021-07-13). If you are not familiar with Scooby Doo, [you can read about it on Wikipedia](https://en.wikipedia.org/wiki/Scooby-Doo).

**1. Import the data.**

```{r}

```

**2. Create a variable that indicates if the culprit was caught by either Scooby or Shaggy. Hint: this involves *caught_scooby* and *caught_shaggy*... you will also want to use the `if_else()` function.**

```{r}

```

**3. Create a variable that is the count of number of times either "zoinks!" or "jeepers!" said in the show. Hint: this involves *zoinks* and *jeepers*.**

```{r}

```

**4. Model if the culprit was caught by either Scooby or Shaggy (the variable you created in Q2) as a function of the number of times either "zoinks!" or "jeepers!" was said on the show (the variable you created in Q3), if Scrappy Doo was in the episode (*scrappy_doo*), and the number of snacks eaten during the episode (*number_of_snacks*). Remember to typeset your model.**

```{r}

```

**5. Find the odds ratios for the model in Q4.**

```{r}

```

**6. Find the 95% confidence intervals for the odds ratios found in Q5.**

```{r}

```

**7. Provide brief interpretations for the odds ratios found in Q5.**



**8. Is this a significant regression line? Test at the $\alpha=0.05$ level. You do not need to typeset your results, but you must provide statistical justification (in writing, not R output).**

```{r}

```

**9. Which, if any, are significant predictors of if the culprit was caught by either Scooby or Shaggy? Test at the $\alpha=0.05$ level. You do not need to typeset your results, but you must provide statistical justification (in writing, not R output).**

```{r}

```

**10. Construct a data visualization to help you explain model results.**

```{r}

```








