---
title: "STA6235 Week 10"
author: "Your Name Here"
format: 
  html:
    self-contained: true
execute:
  echo: true
  warning: false
  message: false
  error: true
editor: source
---

This week we will re-analyze the political data used in class.

**1. Import the data.**

```{r}

```

**2. Remove the outlier as discovered in lecture.**

```{r}

```

**3. Recreate the model from lecture using Poisson regression.**

```{r}

```

**4. Use the appropriate hypothesis test(s) to determine if the interaction between party affiliation and year is significant. Test at the** $\alpha=0.05$ **level. Remember to typeset the results.**

```{r}

```

**5. Use the appropriate hypothesis test(s) to determine if the interaction between party affiliation and region is significant. Test at the** $\alpha=0.05$ **level. Remember to typeset the results.**

```{r}

```

**6. Stratify the resulting models into models for the year 1983 and, separately, the year 2012. Note: you do not have to use R for this.**



**7. State and check the assumptions of Poisson regression.**

```{r}

```

**8. Use the appropriate hypothesis test(s) to determine if the interaction between party affiliation and year is significant. Test at the** $\alpha=0.05$ **level. Remember to typeset the results.**

```{r}

```

**9. Use the appropriate hypothesis test(s) to determine if the interaction between party affiliation and region is significant. Test at the** $\alpha=0.05$ **level. Remember to typeset the results.**

```{r}

```

**10. Stratify the resulting models into models for the year 1983 and, separately, the year 2012. Note: you do not have to use R for this.**

## Combined Questions

**11. Pick a model from either question 6 or 10 provide interpretations for the IRRs.**

```{r}

```

**12. Compare your models side by side. Are you drawing different conclusions? Is the overall message conveyed with the model different?**

**13. Create a visualization for either the Poisson or negative binomial model. Create lines for southern republicans and democrats. Have the year on the $x$-axis.**

```{r}

```
