---
title: "Quiz 9 (in class)"
author: "Your Name Here"
date: '2022-03-09'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(gsheet)

data <- as_tibble(gsheet2tbl("https://docs.google.com/spreadsheets/d/1P5HkpCMmagYQUp0utPMPQBJi1i9nxYVNUyx0mgaHFzc/edit?usp=sharing"))

Y <- data$Sell

X1 <- data$Difficulty_num
```

## Create the design matrix

```{r}
ones <- c(rep(1, length(X1)))
X <- cbind(ones, X1)
head(X)
```

## Find the estimates for $\beta_0$ and $\beta_1$

```{r}
Y <- as_vector(Y)
b <- solve(t(X)%*%X) %*% t(X)%*%Y
b
```

## Determine if $X$ is a significant predictor of $Y$ (construct the test statistic using the matrix approach)

### Using *F* test

```{r}
H = X%*%solve(t(X) %*% X)%*%t(X)
J <- matrix(1, nrow(X), nrow(X))
I <- diag(nrow(X))
SSR <- t(Y) %*% (H - (1/nrow(X)) * J) %*% Y
SSE <- t(Y) %*% (I - H) %*% Y
SST <- SSR + SSE
MSR <- SSR/(ncol(X)-1)
MSE <- SSE*(1/(nrow(X)-(ncol(X)-1)-1))
F <- MSR / MSE
p <- pf(F, ncol(X)-1, nrow(X)-2, lower.tail = FALSE)
```

**Hypotheses**

&emsp;&emsp; $H_0: \ \beta_1 = 0$ <br>
&emsp;&emsp; $H_1: \ \beta_1 \ne 0$

**Test Statistic**

&emsp;&emsp; $F = `r round(F, digits=2)`$.

***p*-value**

&emsp;&emsp; $p = `r p`$.

**Rejection Region**

&emsp;&emsp; Reject if $p < \alpha$, where $\alpha=0.05$.

**Conclusion and Interpretation**

&emsp;&emsp; Reject $H_0$. There is sufficient evidence to suggest that the slope is non-zero.


### Using *t* test

```{r}
# using t test
s2_b <- as.numeric(MSE) * solve(t(X) %*% X) 
se <- c(sqrt(s2_b[1,1]), sqrt(s2_b[2,2]))
t <- b / se
p <- 2*pt(-(abs(t[2])), nrow(X)-(ncol(X)-1)-1, lower.tail = TRUE)
```

**Hypotheses**

&emsp;&emsp; $H_0: \ \beta_1 = 0$ <br>
&emsp;&emsp; $H_1: \ \beta_1 \ne 0$

**Test Statistic**

&emsp;&emsp; $t = `r round(t[2], digits=2)`$.

***p*-value**

&emsp;&emsp; $p = `r p`$.

**Rejection Region**

&emsp;&emsp; Reject if $p < \alpha$, where $\alpha=0.05$.

**Conclusion and Interpretation**

&emsp;&emsp; Reject $H_0$. There is sufficient evidence to suggest that the slope is non-zero.

### Comparing to lm() function

```{r}
summary(lm(Sell ~ Difficulty_num, data = data))
```
